---
output:
  html_document:
    theme: cosmo
---

## Statistics for Genomic Data Science

**Instructor:** [Jeff Leek](http://www.jtleek.com/)


**Class Website:**

* [Statistics for Genomic Data Science](https://www.coursera.org/course/genstats)
* [Genomic Data Science Specialization](https://www.coursera.org/specialization/genomics/41)


**Resources:**

* [Rstudio](http://www.rstudio.com/), [R project](http://www.r-project.org/), and [Bioconductor](http://bioconductor.org/)
* [Rstudio's cheatsheets](http://www.rstudio.com/resources/cheatsheets/) 
* [PH525x Statistics for Genomics Book](http://genomicsclass.github.io/book/)


**Course Materials**


| Week  | Lecture  |  Video | Notes | Code |
|---|---|---|---|---|
| 1 | | |  |  |
|---|---|---|---|---|


**Course R package**

You can get all of the code used in the class by installing the R package:

```{r eval=FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite("devtools")    # only if devtools not yet installed
biocLite("jtleek/genstats")
```

You can see the list of lecture notes and open them using the vignette command:

```{r eval=FALSE}
vignette(package="genstats")
vignette("rmarkdown")
```


<!-- Add links to the rest of the material as we go



-->

**Miscellaneous**

Feel free to submit typos/errors/etc via the github repository associated with the class: 
https://github.com/jtleek/genstats_site

This web-page is modified from Andrew Jaffe's [Summer 2015 R course](http://www.aejaffe.com/summerR_2015/), which also has great material if you want to learn R. 

```{r, eval = FALSE, echo = FALSE}
## Render this file:
rmarkdown::render('index.Rmd')
```

This page was last updated on `r Sys.time()` Eastern Time.
