---
output:
  html_document:
    theme: cosmo
---

## Statistics for Genomic Data Science

**Instructor:** [Jeff Leek](http://www.jtleek.com/)


**Class Website:**

* [Statistics for Genomic Data Science](https://www.coursera.org/course/genstats)
* [Genomic Data Science Specialization](https://www.coursera.org/specialization/genomics/41)


**Resources:**

* [Rstudio](http://www.rstudio.com/), [R project](http://www.r-project.org/), and [Bioconductor](http://bioconductor.org/)
* [Rstudio's cheatsheets](http://www.rstudio.com/resources/cheatsheets/) 
* [PH525x Statistics for Genomics Book](http://genomicsclass.github.io/book/)


**Course Materials**


| Week  | Lecture  |  Video | Notes | Code |
|---|---|---|---|---|
| 0 | About this course | | [Google Slides](https://docs.google.com/presentation/d/1M64qJM4nWCGSqfoIvFOYTmef7R38qz9XrWvS09qHowQ/edit?usp=sharing) [pdf](lecture_notes/00_01_About this course.pdf)| NA  |
| 0 | What is statistics? | | [Google Slides](https://docs.google.com/presentation/d/1Ct_5FOgfRPIxu2apxDBQBvuMHznsPZcykllQMjvcx0A/edit?usp=sharing) [pdf](lecture_notes/00_02_What is statistics-.pdf)| NA  |
| 0 | Knowing what to trust and getting help | | [Google Slides](https://docs.google.com/presentation/d/1wPwjXKsFct3tr20fzWCnE32kCRriieeV7HrcY7kQrtw/edit?usp=sharing) [pdf](lecture_notes/00_03_Knowing what to trust and getting help.pdf)| NA  |
|---|---|---|---|---|
| 1 | Week 1 Introduction | | [Google Slides](https://docs.google.com/presentation/d/1sWtpWd-BvWVDIUlk0McCIqHfPVNG_3J-Ybef71PmGec/edit?usp=sharing) [pdf](lecture_notes/01_01_Week1_Introduction.pdf) | NA  |
|---|---|---|---|---|
| 2 | Week 2 Introduction | | [Google Slides](https://docs.google.com/presentation/d/1Gz-sRPlpAdZKVJ9QayOSSCCSjzn15clPWnafWjP2PXQ/edit?usp=sharing) [pdf](lecture_notes/02_01_Week2_Introduction.pdf) | NA  |
|---|---|---|---|---|
| 3 | Week 3 Introduction | | [Google Slides](https://docs.google.com/presentation/d/133fCjZduCBkK-EjU6sawPGVH-Gu61DWsiDMwBN3oCdY/edit?usp=sharing) [pdf](lecture_notes/03_01_Week3_Introduction.pdf) | NA  |
|---|---|---|---|---|
| 4 | Week 4 Introduction | | [Google Slides](https://docs.google.com/presentation/d/1sV8oS8ivmub7SQ_YUSyAqbqZ5xjgu5m3MzcNgjlRRW0/edit?usp=sharing) [pdf](lecture_notes/04_01_Week4_Introduction.pdf) | NA  |
|---|---|---|---|---|
| Wrapup | Course Wrap-up | | [Google Slides](https://docs.google.com/presentation/d/1DNrW5ZN17zsEXnwOWIVVVQ7VYSNqOO9wUKXuHDfw6TQ/edit?usp=sharing) [pdf](lecture_notes/05_01_WrapUp.pdf) | NA  |
|---|---|---|---|---|


**Course R package**

You can get all of the code used in the class by installing the R package:

```{r eval=FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite("devtools")    # only if devtools not yet installed
biocLite("jtleek/genstats")
```

You can see the list of lecture notes and open them using the vignette command:

```{r eval=FALSE}
vignette(package="genstats")
vignette("rmarkdown")
```


<!-- Add links to the rest of the material as we go



-->

**Miscellaneous**

Feel free to submit typos/errors/etc via the github repository associated with the class: 
https://github.com/jtleek/genstats_site

This web-page is modified from Andrew Jaffe's [Summer 2015 R course](http://www.aejaffe.com/summerR_2015/), which also has great material if you want to learn R. 

```{r, eval = FALSE, echo = FALSE}
## Render this file:
rmarkdown::render('index.Rmd')
```

This page was last updated on `r Sys.time()` Eastern Time.
